Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-03 paper/main.tex
some progress in section 3.4

\begin{abstract}
  \emph{Transition-based Emerson-Lei automata (TELA)} become a popular
  formalism that generalizes many traditional kinds of automata over
  infinite words including Büchi, co-Büchi, Rabin, Streett, and parity
  automata. Transitions in a TELA are labelled with acceptance marks
  and its accepting formula is a positive Boolean combination of terms
  saying that a particular mark has to be visited infinitely or
  finitely often. % in an accepting run.
  Algorithms processing these automata are often very sensitive to the
  number of %different
  acceptance marks. We introduce a new technique reducing the number
  of %different
  acceptance marks in TELA with use of \emph{quantified Boolean
    formulas (QBF)}.
  % : if a constructed QBF formula is satisfiable then
  % its model encodes an equivalent accepting formula with less
  % acceptance marks.
  In fact, we present three formula constructions
  trading speed for higher reduction
  efficiency. We evaluated our reduction technique on TELA produced by
  state-of-the-art tools Delag, ltl3tela, Rabinizer~4, and Spot. The
  technique reduced some acceptance marks in automata produced by all
  these tools. In the case of Rabinizer~4, the cumulative number of
  acceptance marks was reduced to less than one half.
\end{abstract}

@@

\subsection{Optimizations}

@@

>>>>

\begin{abstract}
  \emph{Transition-based Emerson-Lei automata (TELA)} become a popular
  formalism that generalizes many traditional kinds of automata over
  infinite words including Büchi, co-Büchi, Rabin, Streett, and parity
  automata. Transitions in a TELA are labelled with acceptance marks
  and its accepting formula is a positive Boolean combination of terms
  saying that a particular mark has to be visited infinitely or
  finitely often. % in an accepting run.
  Algorithms processing these automata are often very sensitive to the
  number of %different
  acceptance marks. We introduce a new technique reducing the number
  of %different
  acceptance marks in TELA with use of \emph{quantified Boolean
    formulas (QBF)}.
  % : if a constructed QBF formula is satisfiable then
  % its model encodes an equivalent accepting formula with less
  % acceptance marks.
  In fact, we present three formula constructions
  trading speed for higher reduction
  efficiency. We evaluated our reduction technique on TELA produced by
  state-of-the-art tools Delag, ltl3tela, Rabinizer~4, and Spot. The
  technique reduced some acceptance marks in automata produced by all
  these tools. In the case of Rabinizer~4, the cumulative number of
  acceptance marks was reduced to less than one half. \todo{Sazet ltl3tela a jine tooly vsude jako \texttt{ltl3tela} apod?}
\end{abstract}

@@

\subsection{SCC-based optimization}

Now we present a formula optimization based on the fact that every
cycle is completely included in the transition set $\delta_S$ of some
SCC $S$. Note that we cannot reduce the number of acceptance marks in
each SCC separately as all SCCs have to share one acceptance formula.
However, for each SCC we can build a $\Phi_{C,K}$ formula separately and
then we can put all these formulas into one conjunction such that they
share the variables $\vec{i},\vec{f}$.

@@

For a given automaton $\mA=(Q,M,\Sigma,\delta,q_I,\varphi)$, we first
compute all SCCs. Each SCC $S$ induces an automaton $(S,M,\Sigma,q',\delta_S,\varphi)$, where $q'$ is an arbitrary state
of $S$.

the optimization saying that So far, we have not use the fact that each cycle is A
